---
author: "Sean McWeeny"
date: "`r Sys.Date()`"
output: 
  html_document:
    keep_md: false
params: 
  dyad: 107
  trial: 2
title: "`r paste0('ACFs for Asynchronies and ITIs - Dyad ', params$dyad, ', Trial #', params$trial)`"
---



```{r load, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# dyad <- 207
# trial <- 3
x <- readRDS(paste0("C:\\Users\\mcwee\\Documents\\LIVELab\\Social_Drumming\\beh_sync_output\\", params$dyad, "_output.rds"))
show_plots <-  x[[params$trial]][["Exclude Trial"]]
```



**Below is the onset plot, mapped with the per-person ITI on the y-axis.**

```{r Raw Timeseries Plot, echo=FALSE}
print(paste0(params$dyad, " - Trial ", params$trial))
suppressWarnings(plot(x[[params$trial]][["Raw Time Series"]], ))
```

**To do a quick data quality check, we will look at the histogram of the asynchronies.These values should be almost entirely <.2, and several values >.5 may indicate that our data are not correctly aligned.**

```{r data qual, echo=FALSE}
plot(x[[params$trial]][["Async Histogram: Synchronization Phase"]], main = "Asynchronies Histogram: Synchronization Phase")
plot(x[[params$trial]][["Async Histogram: Continuation Phase"]], main = "Asynchronies Histogram: Continuation Phase")

```


**We can take the autocorrelation of these ITIs for each subject. We expect the lag-1 autocorrelation (AC1) to be negative.**

```{r ITI ACFs, echo=FALSE}
plot(x[[params$trial]][["Participant A: ITI ACF - Synchronization Phase"]], main ="Participant A: ITI ACF - Synchronization Phase")
x[[params$trial]][["Participant A: ITI ACF - Synchronization Phase"]]
plot(x[[params$trial]][["Participant A: ITI ACF - Continuation Phase"]], main = "Participant A: ITI ACF - Continuation Phase")
x[[params$trial]][["Participant A: ITI ACF - Continuation Phase"]]

plot(x[[params$trial]][["Participant B: ITI ACF - Synchronization Phase"]], main = "Participant B: ITI ACF - Synchronization Phase")
x[[params$trial]][["Participant B: ITI ACF - Synchronization Phase"]]
plot(x[[params$trial]][["Participant B: ITI ACF - Continuation Phase"]],main="Participant B: ITI ACF - Continuation Phase")

x[[params$trial]][["Participant B: ITI ACF - Continuation Phase"]]
```

**Below, we've plotted the autocorrelation of the asynchronies between the two participants. Here, we expect a positive AC1 value.**

```{r Async ACF, echo=FALSE}
plot(x[[params$trial]][["Async ACF: Synchronization Phase"]], main = "Async ACF: Synchronization Phase")
(x[[params$trial]][["Async ACF: Synchronization Phase"]])

plot(x[[params$trial]][["Async ACF: Continuation Phase"]], main = "Async ACF: Continuation Phase")
(x[[params$trial]][["Async ACF: Continuation Phase"]])


```

**We've also generated some summary information that may be useful in assessing accuracy, precision, and overall tempo.**

```{r summary stats,  echo=FALSE}
print("Continuation Phase BPM")
x[[params$trial]][["Continuation Phase BPM"]]
print("Accuracy: Onset Asynchrony - Synchronization Phase")
x[[params$trial]][["Accuracy: Onset Asynchrony - Synchronization Phase"]]
print("Accuracy: Onset Asynchrony - Continuation Phase")
x[[params$trial]][["Accuracy: Onset Asynchrony - Continuation Phase"]]


print("Precision: Pairwise Asynchrony - Synchronization Phase")
x[[params$trial]][["Precision: Pairwise Asynchrony - Synchronization Phase"]]
print("Precision: Pairwise Asynchrony - Continuation Phase")
x[[params$trial]][["Precision: Pairwise Asynchrony - Continuation Phase"]]

print("N Imputed")
x[[params$trial]][["N Imputed"]]
```

